Understanding the Landscape of Childlessness in the U.S.

### 2024-03-18 outputs/paper/paper.qmd
Last edit

Thus, our estimand is the relationship between age, gender, socio-economic class, educational attainment, health status, marital status and the rate of childlessness in the United States from 1972 to 2022. Through our analysis, we found that childless rate is consistently on the rise from 1972 to 2022, with correlation coefficient of 0.73 between childless percentage and time (or a 6.99% increase over the last 50 years). Factors that directly contribute to this rise are higher educational attainment, higher socio-economic class, lower gender disparity, better health status and dissolution of marriages through divorces, separation and being widowed. In addition, global events like pandemics and recession also heighten the rate of childlessness from 1972-2022, including the AIDs pandemic, 9/11, 2008 Recession and the COVID-19 pandemic. During the 2008 Recession, from 2008 to 2014, the rate of childlessness increases the most, at 3%.

@@

However, this multimodal survey approach also presents several challenges in collecting respondents' opinions on topics such as childbirth and childbearing tendencies, given the private nature of these subjects. With the easy formatting and non-required nature of these surveys, biases like acquiescence bias (only positive responses) might occur because respondents aren't confronted in a face-to-face setting, where many will just opt for a neutral response [@webSurvey]. Therefore, we carefully select various variables to to ensure the authenticity of the public's background on the topic of childlessness, avoiding having the data being too influenced by the changes in surveying methods.

@@

```{r}
#| include: true
#| label: fig-nochild-class-edu
#| fig-cap: Childless Percentage in the US by Class and Educational Attainment (1972-2020)
#| fig-subcap: [Childless percentage by class, Childless percentage by education]
#| layout-ncol: 2
#| warning: false
#| message: false
#| echo: false
#| fig-pos: "t"

@@

\newpage
### Overview of Educational Attainment's Impact on Childlessness

@@

```{r}
#| include: true
#| label: fig-nochild-health-marital
#| fig-cap: Childless Percentage in the US over Time by Marital and Health Status (1972-2020)
#| fig-subcap: [Childless percentage by health, Childless percentage by marital status]
#| layout-ncol: 2
#| warning: false
#| message: false
#| echo: false
#| fig-pos: "t"

@@

Upon assessing the available data, we further extrapolate on them here by calculating the average rate of childlessness in each year for each of these four critical factors: health conditions, marital status, educational attainment and socio-economic class. At the end, @fig-overall compounds on these factors as a graph that shows the overall rate of childlessness in each year from 1972 to 2022.

@@

(@) If yes, How many children have you ever had? Please count all that were born alive at any time (including any you had from a previous marriage).
(short answer text)

@@

3. Are you currently--married, widowed, divorced, separated, or have you never been married? (short answer text)

@@

6. If you were asked to use one of four names for your social class, which would you say you belong in: the lower class, the working class, the middle class, or the upper class? (short answer text)

7. Would you say your own health, in general, is excellent, good, fair, or  poor? (short answer text)

>>>>

Thus, our estimand is the relationship between age, gender, socioeconomic class, educational attainment, health status, marital status, and the rate of childlessness in the United States from 1972 to 2022. Through our analysis, we found that the childless rate is consistently on the rise from 1972 to 2022, with a correlation coefficient of 0.73 between the childless percentage and time (or a 6.99% increase over the last 50 years). Factors that directly contribute to this rise are higher educational attainment, higher socioeconomic class, lower gender disparity, better health status and dissolution of marriages through divorces, separation and being widowed. In addition, global events like pandemics and recessions also heighten the rate of childlessness from 1972-2022, including the AIDs pandemic, 9/11, 2008 Recession and the COVID-19 pandemic. During the 2008 Recession, from 2008 to 2014, the rate of childlessness increases the most, at 3%.

@@

However, this multimodal survey approach also presents several challenges in collecting respondents' opinions on topics such as childbirth and childbearing tendencies, given the private nature of these subjects. With the easy formatting and non-required nature of these surveys, biases like acquiescence bias (only positive responses) might occur because respondents aren't confronted in a face-to-face setting, where many will just opt for a neutral response [@webSurvey]. Therefore, we carefully select various variables to ensure the authenticity of the public's background on the topic of childlessness, avoiding having the data being too influenced by the changes in surveying methods.

@@

```{r}
#| include: true
#| label: fig-nochild-class-edu
#| fig-cap: Childless Percentage in the US by Class and Educational Attainment (1972-2020)
#| fig-subcap: [Childless percentage by class, Childless percentage by education]
#| layout-ncol: 2
#| warning: false
#| message: false
#| echo: false

@@

### Overview of Educational Attainment's Impact on Childlessness

@@

```{r}
#| include: true
#| label: fig-nochild-health-marital
#| fig-cap: Childless Percentage in the US over Time by Marital and Health Status (1972-2020)
#| fig-subcap: [Childless percentage by health, Childless percentage by marital status]
#| layout-ncol: 2
#| warning: false
#| message: false
#| echo: false

@@

Upon assessing the available data, we further extrapolate on them here by calculating the average rate of childlessness in each year for each of these four critical factors: health conditions, marital status, educational attainment and socioeconomic class. At the end, @fig-overall compounds on these factors as a graph that shows the overall rate of childlessness in each year from 1972 to 2022.

@@

(@) If yes, how many children have you ever had? Please count all that were born alive at any time (including any you had from a previous marriage).
(short answer text)

@@

3. Are you currently--married, widowed, divorced, separated, or have you never been married?

- Married
- Widowed
- Divorced
- Separated
- Never been married

@@

6. If you were asked to use one of four names for your social class, which would you say you belong in: the lower class, the working class, the middle class, or the upper class?

- Lower class
- Working class
- Middle class
- Upper class

7. Would you say your own health, in general, is excellent, good, fair, or poor?

- Excellent
- Good
- Fair
- Poor
